### 2023-10-16 ms.qmd
Updates

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2)

@@

>>>>

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)

@@

```{r, models}
#| label: dataclean
#| echo: false
#| warning: false

null <- glmer(FC_associative ~ 1 + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
install.packages("lmtest")
library(lmtest)
lrtest(null, GMM_deli)
anova(GMM_deli)
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group))
print(plot_deli)
```
